### 2017-07-06 Bright_Stars/Submission/submission.tex

% WATERMARKS
%\usepackage{draftwatermark}
%\SetWatermarkText{Preprint}
%\SetWatermarkScale{3}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric B. Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 \& George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As a proof of principle, we have conducted a case study of five anti-cancer therapeutics. We have linked the work of roughly 237,000 authors in 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

%\linenumbers

@@

\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration (FDA) was selected for this study (Table 1). Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively. For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below. An allowance of 2 months was also made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (Table 1).

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}}
\vspace{2 mm}
\caption{
{\bf Case Studies of Five Anti-Cancer Agents} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The unique identifier for each therapeutic is an FDA assigned NDA or BLA number. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column.}
%\begin{flushleft}  
%\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs. The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
\end{tabular}
}
\vspace{2.5 mm}
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases} Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods). Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid). Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field} 
\label{table2}
\end{adjustwidth}
\end{table}

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and gRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and gRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{citing_pmid.png}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{cited_sid.png}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.  \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
\end{adjustwidth}
\end{figure}

The intersection of all five networks consists of 14 publications out of a total of 106,720 unique Scopus identifiers (Supplemental Data, Table 1). Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig. 2. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1.3}{
\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The arcs of blue nodes identify first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\includegraphics[scale=0.1]{proj_percent.png}
\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods). 19,104 unique project numbers were identified as sources of support for publications in all five networks. Of these, 112 projects were common to all five networks. Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research. For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals). A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
\label{fig3}
\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information, Table 2). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases. For example, we found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}). These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.

@@

\section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow for critical comments and advice on formalizing definitions. We thank Sydney Gomes and Caitlin Werle for assistance with graphics. We thank Sandeep Somaiya from NETE as well as Daniel Calto and Holly J. Falk-Krzesinski from Elsevier for their support of this project.

%\nolinenumbers

@@

\end{thebibliography}

@@

\paragraph*{S3 Table 2}
\label{S3_Table 2}
{\bf Elite Performers in Networks} 
\end{document}

>>>>

% WATERMARKS
%\usepackage{draftwatermark}
%\SetWatermarkText{Draft}
%\SetWatermarkScale{3}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 \& George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As a proof of principle, we have conducted a case study of five anti-cancer therapeutics. We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

\linenumbers

@@

\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1). Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively. For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below. An allowance of 2 months was also made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (Table I).

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
\textbf{Case Studies of Five Anti-Cancer Agents}}
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & FDA Approval Date & Unique Identifier & US Patent & Publication Date  \\ \hline
$Alemtuzumab$ & May 2001 & BLA: 103948 & US5846534 & Dec 1998\\ \hline
$Imatinib$ & May 2001 & NDA: 021335 & US5521184 &  May 1996 \\ \hline
$Nelarabine$ & Oct 2005 & NDA: 021877 & US5424295 & Jun 1995  \\ \hline
$Ramucirumab$ & Apr 2014 & BLA: 125477 & US7498414 & Mar 2009  \\ \hline
$Sunitinib$ & Jan 2006  & NDA: 021938  & US6573293 & Jun 2003 \\ \hline
\end{tabular}}
\vspace{2.5 mm}
\begin {flushleft} Five anti-cancer therapeutics, with FDA approval dates ranging from 2001 to 2014, were selected as case studies. The unique identifier for each therapeutic is an FDA assigned NDA or BLA number. While multiple patents are typically associated with a drug or biological, the single US patent number displayed represents the primary invention that preceded approval of the therapeutic. The publication date for each patent is listed in the last column.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs. The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study. [which are]

@@

\begin{table}[!ht]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{{\bf Citation Counts and Mapping Between Bibliographic Databases}}
\scalebox{1}{
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
Therapeutic & citing\_pmid count & citing\_sid count & cited\_sid count  & cited\_pmid count  \\ \hline
$Alemtuzumab$ & 599 & 587 (1\%) & 8840 (2\%) & 7071(20\%)\\ \hline
$Imatinib$ & 1380 & 1373(1\%) & 27326(1\%) &  23340(17\%) \\ \hline
$Nelarabine$ & 104 & 104(0\%) & 2476(1\%) & 1990(20\%)  \\ \hline
$Ramucirumab$ & 1820 & 1804(1\%) & 48587(0\%) & 40973(19\%)  \\ \hline
$Sunitinib$ & 1512  & 1509(0\%)  & 33895(0\%) & 28661(15\%) \\ \hline
\end{tabular}
}
\vspace{2.5 mm}
\begin{flushleft}
 Five anti-cancer therapeutics were selected as case studies. A foundational set of references (citing\_pmid) was assembled for each therapeutic from patents, clinical trials, regulatory documents, and the scientific literature (Materials and Methods). Citing\_pmids were mapped to Scopus identifiers (citing\_sid), which were used, in turn, to retrieve cited publications (cited\_sid). Cited\_sids were mapped back to PubMed identifiers (cited\_pmid).The number of  identifiers at each stage of the mapping process is shown along with percentage loss (in parentheses) when mapping across PubMed and Scopus or due to null values in the cited\_sid field.
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
%  \includegraphics[width=.95\linewidth]{}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
 % \includegraphics[width=.95\linewidth]{}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.  \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
\end{adjustwidth}
\end{figure}

The intersection of all five networks consists of 14 publications out of a total of 106,720 unique Scopus identifiers. Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig. 2. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\includegraphics[scale=0.1]{proj_percent.png}
\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods). 19,104 unique project numbers were identified as sources of support for publications in all five networks. Of these, 112 projects were common to all five networks. Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research. For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals). A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
\label{fig3}
\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases. We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}). These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.

@@

 \nolinenumbers

 \section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow for critical comments and advice on formalizing definitions. We thank Sandeep Somaiya from NETE and Holly J. Falk-Krzesinski from Elsevier for their support of this project.

@@

@@

\paragraph*{S3 Table 2}
\label{S3_Table 2}
{\bf Elite Performers in Networks}

\end{thebibliography}
\end{document}
